VM-Centric Snapshot Deduplication for Cloud Data Backup

### 2015-03-07 snapshot_system/mass.tex
prepare for mass conference
re

%with Fault Isolation 
\title{VM-Centric Snapshot Deduplication for Converged Cloud Architectures}
%VM-Centric  Deduplication  with Fault Isolation for Snapshot Backup in the Cloud
\comments{
\authorinfo{Wei Zhang\and Daniel Agun\and Tao Yang}
           {UC Santa Barbara}
           {\{wei,dagun,tyang\}@cs.ucsb.edu}
\authorinfo{Hong Tang}
           {Alibaba Inc.}
           {hongtang@alibaba-inc.com}
\authorinfo{Rich Wolski}
           {UC Santa Barbara}
           {rich@cs.ucsb.edu}
}
 \authorinfo{
   Wei Zhang$^{\star}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  
Hong Tang$^\dagger$}
   {$^\star$University of California at Santa Barbara \ \ \  
   $^\dagger$Alibaba Inc. }
%  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com

@@

\input{paper_abs}

@@

\input{paper_intro}
\input{paper_background}
\input{paper_dedup}
\input{paper_del}
\input{paper_arch}
\input{paper_eval}
\input{paper_conc}

%\linespread{.97} % to squeeeze lines and put figures in same page
\appendix
\input{paper_analysis}
\bibliographystyle{abbrvnat}
\bibliography{library,dedup1}
\end{document}

>>>>

%with Fault Isolation 
\title{VM-Centric Snapshot Deduplication for Cloud Data Backup}
%VM-Centric  Deduplication  with Fault Isolation for Snapshot Backup in the Cloud
\comments{
\authorinfo{Wei Zhang\and Daniel Agun\and Tao Yang}
           {UC Santa Barbara}
           {\{wei,dagun,tyang\}@cs.ucsb.edu}
\authorinfo{Hong Tang}
           {Alibaba Inc.}
           {hongtang@alibaba-inc.com}
\authorinfo{Rich Wolski}
           {UC Santa Barbara}
           {rich@cs.ucsb.edu}
}
 \authorinfo{
   Wei Zhang$^{\ast}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  
Hong Tang$^\dagger$\\
   $^\star$University of California at Santa Barbara \ \ \  \\
   $^\ast$Pure Storage Inc.\ \ \  $^\dagger$Alibaba Inc. }
%  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com

@@

\input{mass_abs}

@@

\input{mass_intro}
\input{mass_background}
\input{mass_dedup}
\input{mass_analysis}
%\input{mass_del}
\input{mass_arch}
\input{mass_eval}
\input{mass_conc}

%\linespread{.97} % to squeeeze lines and put figures in same page
%\appendix
\bibliographystyle{abbrvnat}
\bibliography{library,dedup1}
\end{document}
